### 2013-09-21 abstract.tex
added central gland volume comparisons

\section*{Abstract}
I need a few sentences from the intro here as a lead in...

MR and ARFI imaging datasets were compared with gross pathology measurements
most immediately post radical prostatectomy.  Both imaging modalities showed
moderate correlations (XX $<$ R$^2 < $ XX) between estimated organ volume and
gross pathologic weights and estimated volumes from tri-axial measurements.
ARFI images, on average, over-estimated prostate volumes by XX\% $\pm$ XX\%,
primarily due to over-estimation of the lateral (right-left) dimension of the
prostate.  MR images also over-estimated the prostate volume by XX\% $\pm$
XX\%, again, with a primary over-estimation of the lateral dimension.  MR and
ARFI imaging yielded different estimates of organ eccentricity as
characterized by ratio of the tri-axial measurements, with both imaging
modalities estimating greater degrees of eccentricity, dominated, again, by
lateral axis over-estimation.  Central gland volumes of the prostate were
well-visualized in both imaging modalities INCLUDE MORE QUANTITATIVE DETAILS
HERE.  ARFI imaging of the prostate can accurately delineate the central gland
of the prostate and the boundaries of the capsule, though care must be taken in
delineating the lateral edges of the prostate in the posterior peripheral zone.

>>>>

\section*{Abstract}
Prostate cancer (PCa) is the most common non-cutaneous malignancy among men in
the United States and the second leading cause of cancer related death.  The
use of non-invasive imaging in the evaluation of PCa could lead to improved
diagnosis, risk-stratification, and management.  Magnetic resonance imaging
(MRI) has been available for use in the workup of patients with PCa since the
early 1980s, and recent advances with functional parameters has greatly
improved its clinical diagnostic utility.  Acoustic radiation force impulse
(ARFI) imaging is an ultrasound-based modality that evaluates the mechanical
properties of tissues. ARFI imaging has the potential to aid in PCa diagnosis
and management by evaluating the structural composition of prostate zones and
tumors base on their stiffness.  In this study, MR and ARFI imaging datasets
were compared with gross pathology measurements immediately post radical
prostatectomy.  Both imaging modalities showed moderate correlations (0.39 $<$
R$^2 < $ 0.74) between estimated organ volume and gross pathologic weights and
estimated volumes from tri-axial measurements.  ARFI images, on average,
over-estimated prostate volumes by 36\% $\pm$ 28\% compared to MR images,
primarily due to over-estimation of the lateral (right-left) dimension of the
prostate.  The central zone volumes of the prostate agreed to within 2.1 $\pm$
39.1\% between ARFI and MR imaging.  MR and ARFI imaging yielded different
estimates of organ eccentricity as characterized by ratio of the tri-axial
measurements, with both imaging modalities estimating greater degrees of
eccentricity, dominated, again, by lateral axis over-estimation.  ARFI imaging
of the prostate can accurately delineate the central gland of the prostate and
the boundaries of the capsule, though care must be taken in delineating the
lateral edges of the prostate in the posterior peripheral zone.

### 2013-09-21 fig_mr_arfi_volumes.tex
added central gland volume comparisons

\begin{figure}[htb!]
\centering
\begin{tabular}{ccc}
\includegraphics[width=0.3\linewidth]{figs/mr_arfi_volumes} &
\includegraphics[width=0.3\linewidth]{figs/mr_arfi_volume_diff} &
\includegraphics[width=0.3\linewidth]{figs/mr_arfi_central_total_diff} \\
(a) Central:Peripheral Volume & (b) Total Volume Difference & (c) Central:Total Volume Difference\\
\end{tabular}
\caption{Comparison of MR and ARFI zonal anatomy volume estimates from manually-segmented images.  Total prostate volumes ranged from 19.6--71.0 cm$^3$ based on MR image models (a), with ARFI image models overestimating total prostate volume by 36.7 $\pm$ 27.9\% (b).  ARFI image delineation of the central zone volume relative to total prostate volume showed a mean underestimation of -15.3 $\pm$ 13.0\% (c, green) relative to the MR central gland : total volume ratios (c, blue).}
\label{fig:mr_arfi_volumes} 
\end{figure}

>>>>

\begin{figure}[htb!]
\centering
\begin{tabular}{ccc}
\includegraphics[width=0.3\linewidth]{figs/mr_arfi_volumes} &
\includegraphics[width=0.3\linewidth]{figs/mr_arfi_volume_diff} &
\includegraphics[width=0.3\linewidth]{figs/mr_arfi_central_diff} \\
(a) Central:Peripheral Volume & (b) Total Volume Difference & (c) Central Volume Difference\\
\end{tabular}
\caption{Comparison of MR and ARFI zonal anatomy volume estimates from
    manually-segmented images.  Total prostate volumes ranged from 19.6--71.0
    cm$^3$ based on MR image models (a), with ARFI image models overestimating
    total prostate volume by 36.7 $\pm$ 27.9\% (b).  ARFI image estimation of
    the central zone volume relative to the MR central gland volume varied by
    2.1 $\pm$ 39.0\% (c).  Table~\ref{tab:mr_arfi_volumes} contains the
    individual volume estimates for the entire prostate and the central
    glands.}
\label{fig:mr_arfi_volumes} 
\end{figure}

### 2013-09-21 intro.tex
added central gland volume comparisons

Acoustic radiation force impulse (ARFI) imaging is an ultrasound-based modality
that evaluates the mechanical properties of tissues.~\cite{Nightingale2002}
ARFI imaging has the potential to aid in PCa diagnosis and management by
evaluating the structural composition of prostate zones and tumors base on
their stiffness.  Zhai et al were able to visualize prostatic anatomy by
utilizing ARFI imaging \exvivo. In a second study, Zhai et al. demonstrated the
feasibility of ARFI prostate imaging \inviv\invivo.~\cite{Zhai2012}  However, to the authors’ best
knowledge, there have been no studies to date that compare \invivo ARFI
prostate imaging to other imaging modalities.~\cite{Zhai2010} The goal of this
study was to evaluate the ability of ARFI to distinguish prostate zonal anatomy
\invivo as compared to endorectal T2WI.

>>>>

Acoustic radiation force impulse (ARFI) imaging is an ultrasound-based modality
that evaluates the mechanical properties of tissues.~\cite{Nightingale2002}
ARFI imaging has the potential to aid in PCa diagnosis and management by
evaluating the structural composition of prostate zones and tumors base on
their stiffness.  Zhai et al were able to visualize prostatic anatomy by
utilizing ARFI imaging \exvivo. In a second study, Zhai et al. demonstrated the
feasibility of ARFI prostate imaging \invivo.~\cite{Zhai2012}  However, to the authors’ best
knowledge, there have been no studies to date that compare \invivo ARFI
prostate imaging to other imaging modalities.~\cite{Zhai2010} The goal of this
study was to evaluate the ability of ARFI to distinguish prostate zonal anatomy
\invivo as compared to endorectal T2WI.

### 2013-09-21 results.tex
added central gland volume comparisons

The computed volumes of the prostates from the MR and ARFI imaging data are
presented in Table~\ref{tab:mr_arfi_volumes}.  The subvolumes associated
with the zonal anatomy in each imaging modality was measured
(Figure~\ref{fig:mr_arfi_volumes}(a)), showing an mean overestimation of
total prostate volume of 36.7 $\pm$ 27.9\% by ARFI imaging compared to MR
volumes (Figure~\ref{fig:mr_arfi_volumes}(b)), and a relative
underestimation of the central zone volume relative to the central gland in MR
imaging of -15.3 $\pm$ 13.0 \% (Figure~\ref{fig:mr_arfi_volumes}(c)).

>>>>

The computed volumes of the prostates from the MR and ARFI imaging data are
presented in Table~\ref{tab:mr_arfi_volumes}.  The subvolumes associated with
the zonal anatomy in each imaging modality was measured
(Figure~\ref{fig:mr_arfi_volumes}(a)), showing an mean overestimation of total
prostate volume of 36.7 $\pm$ 27.9\% by ARFI imaging compared to MR volumes
(Figure~\ref{fig:mr_arfi_volumes}(b)), and central gland volumes differed
between ARFI and MR images by 2.1 $\pm$ 39.1\%
(Figure~\ref{fig:mr_arfi_volumes}(c)).
